### 2022-11-14 NSF2022/SupplementaryDocs/suggestedreviewers.tex

\subsubsection*{Fluid Mechanics and Soft Matter}
\begin{tabular}{ll}
Silas Alben & alben@umich.edu \\
Robert Krasny & krasny@umich.edu \\
Saverio Spagnolie \qquad & spagnolie@math.wisc.edu \\
Petial Vlahovska & petia.vlahovska@northwestern.edu \\
Noel Walkington & noelw@andrew.cmu.edu 
\end{tabular}

\subsubsection*{Amphiphiles}
\begin{tabular}{ll}
Andrea Bertozzi & bertozzi@math.ucla.edu \\
Bob Guy & guy@math.ucdavis.edu \\
Alice McGillman \qquad &  \\
Mike Shelley & mshelley@flatironinstitute.org 
\end{tabular}

>>>>

\subsubsection*{Fluid Mechanics and Soft Matter}
\begin{tabular}{ll}
Silas Alben & alben@umich.edu \\
  Paul Atzberger & atzberg@math.ucsb.edu \\
Robert Krasny & krasny@umich.edu \\
Saverio Spagnolie \qquad & spagnolie@math.wisc.edu \\
Petia Vlahovska & petia.vlahovska@northwestern.edu \\
Noel Walkington & noelw@andrew.cmu.edu 
\end{tabular}

\subsubsection*{Amphiphiles}
\begin{tabular}{ll}
Andrea Bertozzi & bertozzi@math.ucla.edu \\
Bob Guy & guy@math.ucdavis.edu \\
Mike Shelley & mshelley@flatironinstitute.org 
\end{tabular}
